Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-13 report/report.tex
Include personal info and fix toc

\title{Quality Assesment of OpenStreetMap Footpath Data for 3D City Modelling}
\alttitle{Detta är den svenska översättningen av titeln}
\author{Alexander Hjelm}
\email{osquar@kth.se}
\supervisor{Lotta Larsson}
\examiner{Lennart Bladgren}
\hostcompany{Företaget AB} % Remove this line if the project was not done at a host company
\programme{Master in Computer Science}
\school{School of Electrical Engineering and Computer Science}
\date{\today}

@@

\newpage
\setlength{\parskip}{0em}
\tableofcontents
\setlength{\parskip}{1em}
\newpage

\section{Introduction}

@@

% After wednesday meeting with Chris
% TODO: Figure detailing the steps in the point-matching algorithm
% TODO: Edge distance algorithm, outline, algorithm + picture
% TODO: Spell check
% TODO: Go over report one final time

>>>>

\title{Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation}
\alttitle{Kvalitetiv undersökning av OpenStreetMaps gångvägsdata för stadsmodellering i 3D}
\author{Alexander Hjelm}
\email{aljhelm@kth.se}
\supervisor{Christopher Peters}
\examiner{Jonas Beskow}
%\hostcompany{Företaget AB} % Remove this line if the project was not done at a host company
\programme{Master in Computer Science}
\school{School of Electrical Engineering and Computer Science}
\date{\today}

@@

%\newpage
%\setlength{\parskip}{0em}
%\tableofcontents
%\setlength{\parskip}{1em}
%\newpage

\chapter{Introduction}

@@

% After next meeting with Chris
% TODO: Figure detailing the steps in the point-matching algorithm
% TODO: Edge distance algorithm, outline, algorithm + picture
% TODO: Spell check
% TODO: Go over report one final time
% TODO: Swedish abstract
